Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-06-29 article.tex
Revisions

\abstractsection{Significance}
Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) and multi-exposure speckle imaging (MESI) instruments. The selection of the flow control system is critical for the reliable generation of flow during accuracy and sensitivity testing. The majority of recent LSCI studies using microfluidics used syringe pump flow control systems.

\abstractsection{Aim}
We quantified the uncertainty in flow generation for a syringe pump and a pressure-regulated flow system. We then assessed the performance of both LSCI and MESI using the pressure-regulated flow system across a range of physiologically-relevant flow speeds.

\abstractsection{Approach}
The syringe pump and pressure-regulated flow systems were evaluated during stepped flow profile experiments in a microfluidic device using an inline flow sensor. The uncertainty associated with each flow system was calculated and used to determine the reliability for LSCI instrument testing. The pressure-regulated flow system was then used to characterize the relative performance of LSCI and MESI during stepped flow profile experiments while using the inline flow sensor as reference.

@@

% Include a list of up to six keywords after the abstract
\keywords{laser speckle contrast imaging, multi-exposure speckle imaging, flow measurement, microfluidic, flow system}

@@

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020,Sullender.2022} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

Due to its popularity, LSCI (and MESI) instrument development is an active area of research with microfluidic studies commonly used to characterize performance in controlled flow environments. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) substrate \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Arias-Cruz.2019}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, or epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el,Arias-Cruz.2019} or whole blood \cite{Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}. This speed can be converted to a volumetric flow rate using the cross-sectional area of the flow channel, which is then used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump flow control system.

Pressure-driven flow regulation systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate. In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device. Thermal mass flow sensors are commonly used to measure the low flow rates found in microfluidics. These sensors use heating and temperature-sensing elements to detect the magnitude and direction of flow and are factory-calibrated to measure absolute flow rates for various fluids. Integration of the flow sensor with a feedback loop allows for the programming of specific flow rates rather than pressure levels.

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing optical imaging techniques with microfluidic studies.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimicked tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for 45 -- 60 minutes, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 G blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid. A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

@@

A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution. Based on Ref. \cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$. By using a 7\% by volume mixture of the polystyrene microsphere solution and UFDI water (for example, a 10 mL batch of the blood mimicking solution would be made up of 0.7 mL of the 5100A solution and 9.3 mL UFDI water) we are able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$. However, we note that the anisotropy of the microspheres in our solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$). The blood-mimicking solution was preferred over whole blood for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water. Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid. The solution of microspheres was freshly mixed before each experiment to reduce aggregation of particles in the dilution. Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.

@@

The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the inner diameter of the syringe (14.5 mm) to ensure correct flow rate output. It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller (MFCS-EZ with 69 mbar channel, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The MAESFLO control software used feedback from the inline flow sensor to regulate the air pressure to achieve the desired flow rate.

% Figure 2 - LSCI System Schematic + Syringe Pump and Pressure Flow System
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure2.pdf}
    \caption {
        (a) LSCI system schematic for microfluidic flow assessment. A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements. Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system. The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
    }
    \label{fig:system_lsci}
\end{figure}

@@

% Figure 3 - MESI System Schematic
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure3.pdf}
    \caption {
        System schematic for microfluidic flow assessment of MESI and LSCI measurements using only the pressure-regulated flow system.
    }
    \label{fig:system_mesi}
\end{figure}

@@

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI measurements were extracted from the MESI dataset \textit{post hoc}. The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets. The experiment was repeated a total of four times across two days.

@@

Fig.~\ref{fig:error} summarizes the accuracy of the MESI and LSCI measurements at each flow step aggregated across all four trials. The absolute error for MESI was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it increased to almost 9\%. In contrast, the LSCI error was over 8.2\% for all flow speeds, increasing to over 17\% for flow speeds greater than 4 mm/s. Aggregated across all flow speeds, the average absolute error for MESI was 4.6 $\pm$ 2.6\% and LSCI was 15.7 $\pm$ 4.6\%. \textcolor{red}{Does it make sense reporting the numbers this way?}

@@

Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps. This study corroborates previous work \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies. Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials. Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the flow measurements, making it more difficult to properly characterize a system. For example, the flow profiles in Fig. \ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump. These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig. \ref{fig:SvP-FS_LSCI}a. Such instability would increase the uncertainty in the true performance of any instrument being evaluated. The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.

@@

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. \textcolor{red}{Compare to previous measurements by Shams? Can we suggest that the slightly lower errors could be caused by using syringe pump systems?} While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to estimate $\tau_c$. This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s. \textcolor{red}{Can we actually claim this? If yes, then what exactly is happening? Is it just changes in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

@@

This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies. While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems. We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics. We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds. We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI. Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively. Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than random or systematic error. Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.

>>>>

\abstractsection{Significance}
Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) instruments. The selection of the flow control system is critical for the reliable generation of flow during testing. The majority of recent LSCI studies using microfluidics used syringe pumps for flow control.

\abstractsection{Aim}
We quantified the uncertainty in flow generation for a syringe pump and a pressure-regulated flow system. We then assessed the performance of both LSCI and multi-exposure speckle imaging (MESI) using the pressure-regulated flow system across a range of flow speeds.

\abstractsection{Approach}
The syringe pump and pressure-regulated flow systems were evaluated during stepped flow profile experiments in a microfluidic device using an inline flow sensor. The uncertainty associated with each flow system was calculated and used to determine the reliability for instrument testing. The pressure-regulated flow system was then used to characterize the relative performance of LSCI and MESI during stepped flow profile experiments while using the inline flow sensor as reference.

@@

% Include a list of up to six keywords after the abstract
\keywords{laser speckle contrast imaging, multi-exposure speckle imaging, dynamic light scattering, flow measurement, microfluidic, flow system}

@@

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020,Sullender.2022} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

Due to its popularity, LSCI instrument development is an active area of research with microfluidic studies commonly used to characterize performance in controlled flow environments. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) substrate \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Arias-Cruz.2019}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, or epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el,Arias-Cruz.2019} or whole blood \cite{Miao:2014} is then flowed through the channel at controlled rates and imaged using LSCI. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of flow speeds that corresponds with experimentally measured capillary speeds \cite{Tomita:2008do}. This speed can be converted to a volumetric flow rate using the cross-sectional area of the flow channel, which is then used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system.

Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate. In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device. Thermal mass flow sensors are commonly used to measure the low flow rates found in microfluidics. These sensors use heating and temperature-sensing elements to detect the magnitude and direction of flow and are factory-calibrated to measure absolute flow rates for various fluids. Integration of the flow sensor with a feedback loop allows for the programming of specific flow rates rather than pressure levels.

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing flow measurement techniques with microfluidic studies.

@@

\subsection{Microfluidic Phantom Fabrication}
\label{sect:methods_phantom}
The microfluidic flow phantom was cast using PDMS (Sylgard 184™, Dow Corning) with 1.8 mg titanium dioxide (\ce{TiO2}) added per gram of PDMS to generate a scattering background that mimics tissue optical properties ($\mu_s' = 8$ cm$^{-1}$) \cite{Parthasarathy:2008el,Yaroslavsky:2002tg}. The PDMS \ce{TiO2} mixture was vigorously mixed for 15 minutes to ensure even distribution of the \ce{TiO2} in the phantom. Centrifugation (3000 g relative centrifugal force, 10 minutes) was then performed to de-gas the sample and remove any \ce{TiO2} clumps.

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid. A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

@@

A colloidal mixture of suspended 1 $\mu$m diameter polystyrene microspheres (10\% w/w, 5100A, Thermo Fisher Scientific, Inc.) in ultra-filtered de-ionized (UFDI) water was used as a blood-mimicking solution. Based on Ref. \cite[]{Roggan:1999bz}, the reduced scattering coefficient ($\mu_s'$) of whole blood with hematocrit of 0.5 is approximately 20 cm$^{-1}$. By using a 7\% by volume mixture of the microsphere solution and UFDI water (e.g. 10 mL of blood mimicking solution = 0.7 mL of the 5100A solution + 9.3 mL UFDI water) we were able to achieve a calculated $\mu_s'$ of 19.8 cm$^{-1}$. However, we note that the anisotropy of the microsphere solution is different than that of whole blood ($g = 0.92$ versus $g = 0.98$). The blood-mimicking solution was preferred for several reasons: cleaning and safety, ease of acquisition, and because the flow sensor was factory-calibrated for deionized water. Since the concentration of microspheres was very low (0.7\% by weight in the final suspension), the water calibration of the flow sensor remained valid. The solution of microspheres was freshly mixed before each experiment to reduce particle aggregation. Once mixed, the solution was sonicated for 10 minutes to fully suspend the particles and then de-gassed under vacuum to eliminate air bubbles.

@@

The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate. It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller (MFCS-EZ, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The MAESFLO control software used feedback from the inline flow sensor to regulate the air pressure to achieve the desired flow rate.

% Figure 2 - LSCI System Schematic + Syringe Pump and Pressure Flow System
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure2.pdf}
    \caption {
        (a) LSCI system schematic for microfluidic flow assessment (L = Lens, F = Filter). A commercial flow sensor was placed in series with the inlet tubing for the microfluidic flow phantom to obtain real-time absolute flow measurements. Flow was programmatically controlled using either a (b) syringe pump or (c) pressure-regulated flow system. The software for the pressure flow system used a feedback loop between the flow sensor readings and the pressure controller to regulate air pressure.
    }
    \label{fig:system_lsci}
\end{figure}

@@

% Figure 3 - MESI System Schematic
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figure3.pdf}
    \caption {
        System schematic for microfluidic flow assessment of MESI and LSCI measurements using only the pressure-regulated flow system (A = Aperture, M = Mirror, L = Lens, F = Filter).
    }
    \label{fig:system_mesi}
\end{figure}

@@

A stepped flow profile experiment was conducted using the pressure-regulated flow system to assess the performance of both MESI and LSCI. The flow profile consisted of 19 steps spanning 1 -- 10 mm/s in 0.5 mm/s increments. Each speed was maintained for two minutes with a total duration of 40 minutes, including brief periods of no flow (0 mm/s) at the beginning and end of the profile. MESI measurements were acquired continuously throughout the experiment at the maximum acquisition rate of the system ($\sim$2.5 fps). Single-exposure (0.5 ms) LSCI frames were extracted from the MESI dataset \textit{post hoc}. The initial rise of the first flow step was again used to synchronize the timing of the MESI/LSCI and flow sensor datasets. The experiment was repeated a total of four times across two days.

@@

Fig.~\ref{fig:error} summarizes the accuracy of the MESI and LSCI measurements at each flow step aggregated across all four trials. The absolute error for MESI was below 5\% except for flow speeds between 3.5 to 6 mm/s, where it increased to almost 9\%. In contrast, the LSCI error was over 8.2\% for all flow speeds, increasing to over 17\% for flow speeds greater than 4 mm/s. Aggregated across all tested flow speeds, the average absolute error for MESI was 4.6 $\pm$ 2.6\% and LSCI was 15.7 $\pm$ 4.6\%.

@@

Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps. This study corroborates previous work \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies. Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials. Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the measurements, making it more difficult to properly characterize a system. For example, the flow profiles in Fig. \ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump. These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig. \ref{fig:SvP-FS_LSCI}a. Such instability would increase the uncertainty in the true performance of any instrument being evaluated. The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.

@@

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. \textcolor{red}{Compare to previous measurements by Shams? Can we suggest that the reduced error was caused by the syringe pump?} While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to calculate $\tau_c$. This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s. \textcolor{red}{Can we actually claim this? If yes, then what exactly is happening? Is it just numerical changes in the fitting caused by increases in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

@@

This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies. While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems. We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics. We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds. We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI. Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively. Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than systematic error. Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.
